---
title: "ICM_D"
author: "Zhuofei Xie"
date: "2/13/2020"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(ggplot2)
```

```{r}
passingevents = read.csv("passingevents.csv")
head(passingevents)
```



```{r}
num_row = nrow(passingevents)
num_row_array = c(1:num_row)
passingevents_after_coord <- passingevents
for(i in num_row_array) 
  if(passingevents_after_coord$TeamID[i] != "Huskies"){
    passingevents_after_coord$EventOrigin_x[i] = 100 - passingevents_after_coord$EventOrigin_x[i]
    passingevents_after_coord$EventOrigin_y[i] = 100 - passingevents_after_coord$EventOrigin_y[i]
    passingevents_after_coord$EventDestination_x[i] = 100 - passingevents_after_coord$EventDestination_x[i]
    passingevents_after_coord$EventDestination_y[i] = 100 - passingevents_after_coord$EventDestination_y[i]
  }
head(passingevents_after_coord)
```


```{r}
write.csv(passingevents_after_coord, file = "passingevents.csv")
```


```{r}
fullevents <- read.csv("fullevents_original.csv")
head(fullevents)
```

```{r}
num_row = nrow(fullevents)
num_row_array = c(1:num_row)
fullevents_after_coord <- fullevents
for(i in num_row_array) 
  if(fullevents_after_coord$TeamID[i] != "Huskies"){
    fullevents_after_coord$EventOrigin_x[i] = 100 - fullevents_after_coord$EventOrigin_x[i]
    fullevents_after_coord$EventOrigin_y[i] = 100 - fullevents_after_coord$EventOrigin_y[i]
    fullevents_after_coord$EventDestination_x[i] = 100 - fullevents_after_coord$EventDestination_x[i]
    fullevents_after_coord$EventDestination_y[i] = 100 - fullevents_after_coord$EventDestination_y[i]
  }
head(fullevents_after_coord)
```

```{r}
write.csv(fullevents_after_coord, file = "fullevents.csv")
```

```{r


```{r}
passingevents_MatchID_1 <- passingevents_after_coord %>% 
  filter(MatchID==1)
passingevents_MatchID_1
```


```{r}

ggplot(data = passingevents_MatchID_1, aes(x = EventOrigin_x, y = EventOrigin_y, color = TeamID)) + geom_point()
```

```{r}
passingevents_d1 <- read.csv("passingevents_d1.csv")
head(passingevents_d1)
passingevents_d1
```

MatchID == 1
```{r}

passingevents_d1_1 <- passingevents_d1 %>% 
  filter(MatchID == 1) 
head(passingevents_d1_1)
```


```{r}
passingevents_d1_summary <- passingevents_d1_1 %>% 
  group_by(EventSubType) %>% 
  summarise(
    Average_distace = mean(Passing.Distence)
  )
passingevents_d1_summary
```

```{r}
passingevents_d1_1_corss <- passingevents_d1_1 %>% 
  filter(EventSubType == "Cross" & Passing.Distence > passingevents_d1_summary$Average_distace[1])
passingevents_d1_1_corss
```

```{r}
passingevents_d1_1_HandPass <- passingevents_d1_1 %>% 
  filter(EventSubType == "Hand pass" & Passing.Distence > passingevents_d1_summary$Average_distace[2])
passingevents_d1_1_HandPass
```

```{r}
passingevents_d1_1_HeadPass <- passingevents_d1_1 %>% 
  filter(EventSubType == "Head pass" & Passing.Distence > passingevents_d1_summary$Average_distace[3])
passingevents_d1_1_HeadPass
```

```{r}
passingevents_d1_1_HighPass <- passingevents_d1_1 %>% 
  filter(EventSubType == "High pass" & Passing.Distence > passingevents_d1_summary$Average_distace[4])
passingevents_d1_1_HighPass
```

```{r}
passingevents_d1_1_Launch <- passingevents_d1_1 %>% 
  filter(EventSubType == "Launch" & Passing.Distence > passingevents_d1_summary$Average_distace[5])
passingevents_d1_1_Launch
```
```{r}
passingevents_d1_1_SimplePass <- passingevents_d1_1 %>% 
  filter(EventSubType == "Simple pass" & Passing.Distence > passingevents_d1_summary$Average_distace[6])
passingevents_d1_1_SimplePass
```


```{r}
passingevents_d1_1_SmartPass <- passingevents_d1_1 %>% 
  filter(EventSubType == "Smart pass" & Passing.Distence > passingevents_d1_summary$Average_distace[7])
passingevents_d1_1_SmartPass
```

将单传和双传分成两个数据组
```{r}
passingevents_d1_1
```

```{r}
names <- names(passingevents_d1_1)
D1_single_pass <- data_frame()
index = c(1:(nrow(passingevents_d1_1)-1))

D1_single_pass
```

单传
```{r}
for(i in index){
  if(i == 1){
    if(passingevents_d1_1$DestinationPlayerID[i] != passingevents_d1_1$OriginPlayerID[i+1]){
      D1_single_pass <- rbind(D1_single_pass,passingevents_d1_1[i,])
    }
  }
  else{
    if(passingevents_d1_1$DestinationPlayerID[i] != passingevents_d1_1$OriginPlayerID[i+1] && passingevents_d1_1$OriginPlayerID[i] != passingevents_d1_1$DestinationPlayerID[i-1]){
      D1_single_pass <- rbind(D1_single_pass,passingevents_d1_1[i,])
    }
  }
}
D1_single_pass
```

```{r}
drop_row <- 
  D1_single_pass %>% select(X)

vector_c <- as.vector(drop_row$X)
```


```{r}
passingevents_d1_1[-vector_c,]
```

```{r}
passingevents_d1_1
```


```{r}
passingevents_d1
```

```{r}

```


















